Light inextensible strings (thread) under tension in the Schwarzschild geometry

### 2021-02-25 string_physics_educator_revision3.tex
tidyup
fixes #35

Of course, no real string is perfectly weightless or inextensible.
With tension~$T$, gravitational acceleration $g$ and (proper) mass per
(proper) unit length~$\mu$, then a string will behave as though light
on lengthscales $L\lesssim T/\left(\mu g\right)$.  Using
$c^4/\left(4GM\right)$ for the strength of gravity at the event
horizon of a black hole with mass $M$ gives $L\lesssim TM/\left(\mu
c^4\right)$.  For the string to behave as though light on lengthscales
comparable with the Schwarzschild radius would require $T\gtrsim\mu
c^2$.  Exceeding this criterion would violate the dominant energy
condition (and in this context we note that transverse waves would
propagate at speed~$\sqrt{T/\mu}\sim c$).  Nevertheless, the
idealization of a string as light and inextensible is an interesting
and informative limit: Rindler~\cite{rindler}, for example, considers
lowering a heavy object to the event horizon on the end of such a
string to illustrate energetic arguments in GR.

>>>>

Of course, no real string is perfectly weightless or inextensible.
With tension~$T$, gravitational acceleration $g$ and (proper) mass per
(proper) unit length~$\mu$, then a string will behave as though light
if the weight of the string does not exceed the tension, so that $L\mu g\lesssim T$.
Using
$c^4/\left(4GM\right)$ for the strength of gravity at the event
horizon of a black hole with mass $M$ gives $L\lesssim TM/\left(\mu
c^4\right)$.  For the string to behave as though light on lengthscales
comparable with the Schwarzschild radius would require $T\gtrsim\mu
c^2$.  Exceeding this criterion would violate the dominant energy
condition (and in this context we note that transverse waves would
propagate at speed~$\sqrt{T/\mu}\sim c$).  Nevertheless, the
idealization of a string as light and inextensible is an interesting
and informative limit: Rindler~\cite{rindler}, for example, considers
lowering a heavy object to the event horizon on the end of such a
string to illustrate energetic arguments in GR.
